Improving inference of evolutionary history

### 2015-01-29 slides/osu/slides.tex
Updating osu slides.
Making paths to some of the photos full rather than relative.

\begin{frame}
    \frametitle{Climate-driven diversification}
\begin{columns}[c]
    \column{.5\textwidth}
        \vspace{-1cm}
        \begin{onlyenv}<1>
        \begin{minipage}[t][1.0\textheight][c]{\linewidth}
        \centerline{
        \includegraphics<1>[height=3cm]{../../../../Dropbox/field-photos/people/rafe.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=3cm]{../../../../Dropbox/field-photos/people/cam.jpg}}
        \centerline{
        \includegraphics<1>[height=3cm]{../../../../Dropbox/field-photos/people/charles.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=3cm]{../../../../Dropbox/field-photos/people/jake.jpg}}
        \end{minipage}
        \end{onlyenv}

@@

\begin{frame}
    \frametitle{More data}
    \begin{columns}[c]
        \column{.5\textwidth}
        \begin{myitemize}
            \item Collecting genomic data from two gekkonid radiations
                co-distributed Southeast Asia
            \begin{myitemize}
                \item \emph{Cyrtodactylus}---12+ species
                \item \emph{Gekko}---13+ species
            \end{myitemize}
            \item Whole genome assemblies for each genus
            \item RAD-seq libraries constructed for $\approx150$ individuals
                from each genus
        \end{myitemize}
        \centerline{
        \includegraphics<1->[height=2.5cm]{../../../../Dropbox/field-photos/misc/lee-and-me.jpg}
        \hspace{2mm}
        \includegraphics<1->[height=2.5cm]{../../../../Dropbox/field-photos/people/rafe.jpg}}
        \column{.5\textwidth}
        \includegraphics[width=\textwidth]{../images/photos/cyrt-agusanensis.jpg} \quad
        \includegraphics[width=\textwidth]{../images/photos/gekko-mindorensis.jpg}
    \end{columns}
\end{frame}

@@

\begin{frame}
    \frametitle{More power}
    \centerline{
    \includegraphics<1->[height=2cm]{../../../../Dropbox/field-photos/people/mtholder.jpg}
    \hspace{0.6mm}
    \includegraphics<1->[height=2cm]{../../../../Dropbox/field-photos/people/jeet2.jpg}
    \hspace{0.6mm}
    \includegraphics<1->[height=2cm]{../../../../Dropbox/field-photos/people/vladimir.jpg}
    \hspace{0.6mm}
    \includegraphics<1->[height=2cm]{../images/revbayes.png}}

@@

\begin{frame}
    \frametitle{Future directions: Gobi Desert}
    \vspace{-2mm}
    \begin{columns}
        % \column{\dimexpr\paperwidth-10pt}
        \column{\dimexpr\paperwidth}
        \includegraphics[width=\textwidth]{../../../../Dropbox/field-photos/gobi/mongolia-auto-shop.jpg}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Future directions: Gobi Desert}
    \vspace{-2mm}
    \begin{columns}
        % \column{\dimexpr\paperwidth-10pt}
        \column{\dimexpr\paperwidth}
        \includegraphics[width=\textwidth]{../../../../Dropbox/field-photos/gobi/mongolia-teratoscincus-przewalskii-landscape.jpg}
    \end{columns}
\end{frame}

\begin{frame}[t]
    \frametitle{Future directions: West-Central Africa}
    \begin{center}
        \includegraphics<1->[height={3cm}]{../../../../Dropbox/field-photos/africa/Figure2_WAmapForestDist.png}
        \hspace{0.3mm}
        \includegraphics<1->[height={3cm}]{../../../../Dropbox/field-photos/africa/Figure4_herps.jpeg}
    \end{center}

    \only<1>{
    \begin{center}
        \includegraphics[height={3.5cm}]{../../../../Dropbox/field-photos/people/adam.png}
        \hspace{0.3mm}
        \includegraphics[height={3.5cm}]{../../../../Dropbox/field-photos/people/fujita.jpg}
    \end{center}
    }

@@

\begin{frame}
    \frametitle{``Micro''-islands of the Sunda Shelf}
    \vspace{-2mm}
    \begin{columns}
        % \column{\dimexpr\paperwidth-10pt}
        \column{\dimexpr\paperwidth}
        \includegraphics[width=\textwidth]{../../../../Dropbox/field-photos/malaysia/malaysia-burungs.jpg}
    \end{columns}
\end{frame}

>>>>

\begin{frame}
    \frametitle{Climate-driven diversification}
\begin{columns}[c]
    \column{.5\textwidth}
        \vspace{-1cm}
        \begin{onlyenv}<1>
        \begin{minipage}[t][1.0\textheight][c]{\linewidth}
        \centerline{
        \includegraphics<1>[height=3cm]{/home/jamie/Dropbox/field-photos/people/rafe.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=3cm]{/home/jamie/Dropbox/field-photos/people/cam.jpg}}
        \centerline{
        \includegraphics<1>[height=3cm]{/home/jamie/Dropbox/field-photos/people/charles.jpg}
        \hspace{0.3mm}
        \includegraphics<1>[height=3cm]{/home/jamie/Dropbox/field-photos/people/jake.jpg}}
        \end{minipage}
        \end{onlyenv}

@@

\begin{frame}
    \frametitle{More data}
    \begin{columns}[c]
        \column{.5\textwidth}
        \begin{myitemize}
            \item Collecting genomic data from two gekkonid radiations
                co-distributed Southeast Asia
            \begin{myitemize}
                \item \emph{Cyrtodactylus}---12+ species
                \item \emph{Gekko}---13+ species
            \end{myitemize}
            \item Whole genome assemblies for each genus
            \item RAD-seq libraries constructed for $\approx150$ individuals
                from each genus
        \end{myitemize}
        \centerline{
        \includegraphics<1->[height=2.5cm]{/home/jamie/Dropbox/field-photos/misc/lee-and-me.jpg}
        \hspace{2mm}
        \includegraphics<1->[height=2.5cm]{/home/jamie/Dropbox/field-photos/people/rafe.jpg}}
        \column{.5\textwidth}
        \includegraphics[width=\textwidth]{../images/photos/cyrt-agusanensis.jpg} \quad
        \includegraphics[width=\textwidth]{../images/photos/gekko-mindorensis.jpg}
    \end{columns}
\end{frame}

@@

\begin{frame}
    \frametitle{More power}
    \centerline{
    \includegraphics<1->[height=2cm]{/home/jamie/Dropbox/field-photos/people/mtholder.jpg}
    \hspace{0.6mm}
    \includegraphics<1->[height=2cm]{/home/jamie/Dropbox/field-photos/people/jeet2.jpg}
    \hspace{0.6mm}
    \includegraphics<1->[height=2cm]{/home/jamie/Dropbox/field-photos/people/vladimir.jpg}
    \hspace{0.6mm}
    \includegraphics<1->[height=2cm]{../images/revbayes.png}}

@@

\begin{frame}
    \frametitle{Future directions: Gobi Desert}
    \vspace{-2mm}
    \begin{columns}
        % \column{\dimexpr\paperwidth-10pt}
        \column{\dimexpr\paperwidth}
        \includegraphics[width=\textwidth]{/home/jamie/Dropbox/field-photos/gobi/mongolia-auto-shop.jpg}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Future directions: Gobi Desert}
    \vspace{-2mm}
    \begin{columns}
        % \column{\dimexpr\paperwidth-10pt}
        \column{\dimexpr\paperwidth}
        \includegraphics[width=\textwidth]{/home/jamie/Dropbox/field-photos/gobi/mongolia-teratoscincus-przewalskii-landscape.jpg}
    \end{columns}
\end{frame}

\begin{frame}[t]
    \frametitle{Future directions: West-Central Africa}
    \begin{center}
        \includegraphics<1->[height={3cm}]{/home/jamie/Dropbox/field-photos/africa/Figure2_WAmapForestDist.png}
        \hspace{0.3mm}
        \includegraphics<1->[height={3cm}]{/home/jamie/Dropbox/field-photos/africa/Figure4_herps.jpeg}
    \end{center}

    \only<1>{
    \begin{center}
        \includegraphics[height={3.5cm}]{/home/jamie/Dropbox/field-photos/people/adam.png}
        \hspace{0.3mm}
        \includegraphics[height={3.5cm}]{/home/jamie/Dropbox/field-photos/people/fujita.jpg}
    \end{center}
    }

@@

\begin{frame}
    \frametitle{``Micro''-islands of the Sunda Shelf}
    \vspace{-2mm}
    \begin{columns}
        % \column{\dimexpr\paperwidth-10pt}
        \column{\dimexpr\paperwidth}
        \includegraphics[width=\textwidth]{/home/jamie/Dropbox/field-photos/malaysia/malaysia-burungs.jpg}
    \end{columns}
\end{frame}
